Optimal (Multiway) Spatial Joins

### 2024-05-19 msj.tex
yufei

In terms of techniques, our primary contribution is a result on the mathematical structure of $k$-SJ. Specifically, for any $n \ge 1$ and $k \ge 2$, define function $F(n, k)$ to return the lowest positive integer such that our $k$-SJ algorithm can solve any instance of the $k$-SJ problem with input size $n$ and output size $\out$ in $F(n, k) + O(\out)$ time. Our main technical contribution can now be stated as:

\begin{theorem} \label{thm:main}
    For any $n \ge 1$ and $k \ge 3$, it holds that 
    \myeqn{
        F(n, k) = O(k^3) \cdot ( F(n, k-1) + n \log n).
        \label{eqn:main:reccurrence}
    }
\end{theorem}

>>>>

In terms of techniques, our primary contribution is a result on the problem's mathematical structure. Fix any $k \ge 3$ and an arbitrary algorithm $\A$ for the $(k-1)$-SJ problem. For any $n \ge 1$, define function $F_{k-1}(n, \out)$ to return the worst-case running time of $\A$ on any instance of the $(k-1)$-SJ problem having input size $n$ and output size $\out$. Our main technical contribution is to establish:

\begin{theorem} \label{thm:main}
    For any $n \ge 1$ and $k \ge 3$, it holds that 
    \myeqn{
        F(n, k, \out) = O(k^3) \cdot \big( F(n, k-1, \out) + n \log n + \out \big).
        \label{eqn:main:reccurrence}
    }
\end{theorem}

The theorem implies the existence of a recursive nature of $k$-SJ.
